The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-03 Writeup/paper_v3.tex
Reason for comparing with Kovac

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.
The classification of overdensities and underdensities agrees with the work done by~\cite{Kovac_Density10k} on the zCOSMOS field using spectra and 3D density field reconstruction , except for the last two high redshift bins.
We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
is observed by us in $z=0.80-0.85$ slice.
\rachel{Say why you are doing this comparison with Kovac et al.}

@@

The PSF correction scheme used on the observed images is that of 're-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}. Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities 
of the galaxies, which we will refer to as `ellipticities based on moments'.

>>>>

We thus identify the regions $z=0.30-0.40, 0.65-0.75, 0.80-0.85$ as overdense, $z=0.55-0.65, 0.75-0.80$ as underdense and $z=0.40-0.55$ as unclassified.

Our classification is not very rigorous since it considers only the counts in redshift slices and compares with models that only approximately describe the redshift distribution of galaxies.
Moreover, the photometric redshifts become less accurate as we go to higher redshifts (cf.~\S\ref{S:data}) and no information about structure in transverse direction has been taken into account.
Thus, it is important to cross-check with a more careful study of the density fields in the same field of view.
~\cite{Kovac_Density10k}, using a sample of $\sim 10,000$ zCOSMOS spectra sources with $I_{AB}<22.5$, have reconstructed the three dimensional overdensity field up to $z\sim 1$.
In spite of the above mentioned shortcomings, our classification of overdensities and underdensities agrees with this work done, except for the last two high redshift bins.
We believe that this disagreement is due to the errors in our photometric redshifts and the overdensity reported in $z=0.875-1$ slice
is observed by us in $z=0.80-0.85$ slice.
\rachel{Say why you are doing this comparison with Kovac et al.} \arun{Done.}

@@

The PSF correction scheme used on the observed images is that of `re-Gaussianization' method described in \S 2.4 of~\cite{HS03} (hereafter HS03).
This method models the true PSF $g({\bf x})$ as a Gaussian $G({\bf x})$ and the residual $\epsilon({\bf x}) = g({\bf x}) - G({\bf x})$ is assumed to be small. Thus, the Gaussian-convolved
intrinsic image of $f$, is $I' = G\otimes f = I - \epsilon \otimes f$, where $I$ is the observed image. The crucial idea here is that, when $\epsilon$ is small, we get a reasonably accurate
estimate of $I'$ even if we use an approximate form for $f$. The form assumed for $f$ is that of a Gaussian with covariance $M_f^{(0)} = M_I - M_g$, where $M_I$ and $M_g$ are the adaptive
covariances of the measured object and PSF respectively, described in \S 2.1 of HS03, which is in turn based on~\cite{BJ02}. Once we obtain the covariance matrices of the instrinsic image $f$, one can compute the ellipticities 
of the galaxies, which we will refer to as `ellipticities based on moments'.
